Arrows for Parallel Computations

### 2017-11-24 paper/content/main.tex
moving things back to the parent folder. only synctex has to be fixed now.
wip
added olegl changes
wip on benchmarks for Torus in the paper
wip restructuring the paper, wip on motivation's contribution
tmp
further restructuring according to Phil's remarks. moved related work to 2

%% add a tweak to polycode, similar to literate in lstlistings, but uglier
%format |>>>|        = "\mathbin{|\!\!>\!\!>\!\!>\!\!|}"
%format parcomp        = "\mathbin{|\!\!>\!\!>\!\!>\!\!|}"
%format >>>        = "\mathbin{>\!\!>\!\!>}"
%% ^^^^ you want this. and similar for ***, +++, etc.
%% a hack for list comprehensions' <-, typeset it as <--
%%%%%format <--        = "\in "
%format DOLLAR = "\mathbin{\$}"
%%%% %format ` = "\`"
%%%% %% works fine without
%format ||| = "\mathbin{\mid\!\mid\!\mid}"
%format pipepipepipe = "\mathbin{\mid\!\mid\!\mid}"
%format |&&&| = "\mathbin{\mid\!\!\&\!\&\!\&\!\!\mid}"
%format parand = "\mathbin{\mid\!\!\&\!\&\!\&\!\!\mid}"
%format &&& = "\mathbin{\&\!\&\!\&}"
%format |***| = "\mathbin{\mid\!\!*\!*\!*\!\!\mid}"
%format parstar = "\mathbin{\mid\!\!*\!*\!*\!\!\mid}"
%format *** = "\mathbin{*\!*\!*}"
%format |+++| = "\mathbin{\mid\!\!+\!\!+\!\!+\!\!\mid}"
%format +++ = "\mathbin{+\!\!+\!\!+}"

%include polycode.fmt

@@

\jdate{April 2017}
\pubyear{2017}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\doi{...}

@@

%include prelude.tex

\title{Arrows for Parallel Computations}
\ifthenelse{\boolean{anonymous}}{%
\author{Submission ID xxxxxx}
}{%
%\author{Martin Braun, Phil Trinder, and Oleg Lobachev}
%\affiliation{University Bayreuth, Germany and Glasgow University, UK}
 \author[M. Braun, P. Trinder and O. Lobachev]%
        {MARTIN BRAUN\\
         University Bayreuth, 95440 Bayreuth, Germany\\
         PHIL TRINDER\\
		 Glasgow University, Glasgow, G12 8QQ, Scotland\\
		 \and\ OLEG LOBACHEV\\
		 University Bayreuth, 95440 Bayreuth, Germany}
}% end ifthenelse

@@

@@

%% environment inside
%include abstract.tex

@@

	%
	%%include abstract.lhs
	%
	%\newpage
	\tableofcontents
	%\pagebreak
	%include motivation.tex
	%include parallelHaskells.tex
	%include arrows.tex
	%\pagebreak
	%include relwork.tex
	%\pagebreak
	%\pagebreak
	%include parrows.tex
	%\pagebreak
	%include basicSkeletons.tex
	%\pagebreak
	%include syntacticSugar.tex
	%\pagebreak
	%include futures.tex
	%\pagebreak
	%include mapSkeletons.tex
	%\pagebreak
	%include topologySkeletons.tex
	%\pagebreak
	%include benchmarks.tex
	%%\pagebreak
	%include conclusion.tex
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	%include utilityFunctions.tex
\end{document}

>>>>

@@

\jdate{August 2017}
\pubyear{2017}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\doi{...}

@@

\input{lhs2TeXSafeCommands}
\input{prelude}

\title{Arrows for Parallel Computations}
\ifthenelse{\boolean{anonymous}}{%
\author{Submission ID xxxxxx}
}{%
%\author{Martin Braun, Phil Trinder, and Oleg Lobachev}
%\affiliation{University Bayreuth, Germany and Glasgow University, UK}
 \author[M. Braun, O. Lobachev and P. Trinder]%
        {MARTIN BRAUN\\
         University Bayreuth, 95440 Bayreuth, Germany\\
		 OLEG LOBACHEV\\
		 University Bayreuth, 95440 Bayreuth, Germany\\
		 \and\ PHIL TRINDER\\
		 Glasgow University, Glasgow, G12 8QQ, Scotland}
}% end ifthenelse

@@

\def\SymbReg{\textsuperscript{\textregistered}}

@@

%% environment inside
\input{abstract.tex}

@@

	%
	%%include abstract.lhs
	%
	%\newpage
	%\pagebreak
	\input{motivation}
	\input{relwork}
	\begin{flushright}

	\end{flushright}\section{Background}
	\label{sec:background}
	\input{arrows}
	\input{parallelHaskells}
	%\pagebreak
	%\pagebreak
	%\pagebreak
	\input{parrows}
	%\pagebreak
	\input{basicSkeletons}
	%\pagebreak
	\input{syntacticSugar}
	%\pagebreak
	\input{futures}
	%\pagebreak
	\input{mapSkeletons}
	%\pagebreak
	\input{topologySkeletons}
	%\pagebreak
	\input{benchmarks}
	%%\pagebreak
	\input{conclusion}
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	\input{utilityFunctions}
\end{document}
